MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
changes
part 2 - Hot Hand Theory

```{r}
df<- read.csv("shot_logs.csv")  #assigning the dataframe to 'df' variables
attach(df) #telling R that this is the dataframe we'll be working with (eliminating the need to use df$ for variables)

#we need to change the format of some of the columns to 'Character'

@@

#SUMMARY OF POINTS
```{r}
ptssum<- cast(df, GAME_ID1+ player_id + player_name ~ PTS); head(ptssum)
#creating "total points per player, per game" column
ptssum$totalpts<- ptssum[,"2"]*2 + ptssum[,"3"]*3

@@

number_of_streaks(shotresult)
#To be continued (probabilities- indipendence, plots, interpret results for specific players(those with higher shot_numbers))
```

>>>>

```{r}
df<- read.csv("shot_logs.csv")  #assigning the dataframe to 'df' variables
attach(df) #telling R that this is the dataframe we'll be working with (eliminating the need to use df$ for variables)
df1 <- read.csv('shot_logs1010.csv')
#we need to change the format of some of the columns to 'Character'

@@

#SUMMARY OF POINTS
```{r}
ptssum<- cast(df1, GAME_ID1+ player_id + player_name  ~ PTS); head(ptssum)
#creating "total points per player, per game" column
ptssum$totalpts<- ptssum[,"2"]*2 + ptssum[,"3"]*3

@@

number_of_streaks(shotresult)

player_and_game <- function(x, y) {
   player <- df[df[ ,'player_id'] == x & df[ ,'GAME_ID1'] == y, 'FGM']
   number_of_streaks(as.vector(player))
}
player_and_game(202681, 21400681)

ourtable <- head(pttsum2,10)

list_streaks <- list()

for(i in ourtable$player_id) {
   streak_per_player <- player_and_game(i, ourtable[ourtable[ ,'player_id'] == i, 'GAME_ID1'])
   print(streak_per_player)
}

#To be continued (probabilities- indipendence, plots, interpret results for specific players(those with higher shot_numbers))
```
